% @file resume.tex
% @author Justin Gallagher, me@justingallag.com
% @since 2015-08-17

\documentclass[]{friggeri-cv}

\usepackage{enumitem}

\newcommand{\starr}{\raisebox{0.2ex}{$\star $}}

\begin{document}
    \header{justin}{gallagher}
    {computer scientist \& software engineer}

    \begin{aside}
        \section{contact}
            (603) 440-3873
            \href{mailto:me@justingallag.com}{me@justingallag.com}
            \href{http://justingallag.com}{justingallag.com}
            \href{https://github.com/justingallagher}{github: justingallagher}
            \href{https://www.linkedin.com/in/justingallag}{linkedin: justingallag}
        \section{languages}
            \starr \ C
            \starr \ C++
            \starr \ C\#
            \starr \ Java
            \starr \ Javascript
            Python
            SQL
            SML
        \section{technologies}
            Android SDK
            Windows SDK
            Node.js
            ASP.NET
            OpenGL
        \section{applications}
            Git
            LaTeX
            Vim
            Microsoft Office
            Visual Studio
            Linux
            Windows
        \section{interests}
            Firmware development
            Robotics
            Operating Systems
            Game Design
    \end{aside}

    \section{education}

    \begin{entrylist}
        \entry
            {since 2013}
            {Carnegie Mellon University, {\normalfont expected graduation May 2016}}
            {Pittsburgh, PA}
            {Bachelor of Science, Computer Science \& Business Administration Minor\\
            \textbf{GPA}: 3.83/4.00 \ \ \ \textbf{Dean's List}: Fall 2013, Fall 2014, Spring 2015}
        \entrys
            {2009--2013}
            {Phillips Exeter Academy, {\normalfont English Diploma, \emph{cum laude}}}
            {Exeter, NH}
            {}
    \end{entrylist}

    \section{technical experience}

    \begin{entrylist}
        \entrys
            {2015}
            {Microsoft Corporation, {\normalfont Software Engineer Intern}}
            {Redmond, WA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Designed and implemented an analytics tool which allows hierarchical search of XAML file structure using C\# and SQL.
                \item[-] Leveraged telemetry data to actively track the reliability of Windows Phone applications, leading to the discovery of a ship-blocking bug.
             \end{itemize}}
        \entrys
            {2014}
            {Microsoft Corporation, {\normalfont Explorer Intern}}
            {Redmond, WA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Developed a dashboard for telemetry data, enabling managers to make actionable, data-backed decisions about Microsoft Office Online features.
                \item[-] Worked on a team of 3 interns to create a responsive ASP.NET web application capable of accessing large amounts of SQL data.
             \end{itemize}}
        \entrys
            {since 2013}
            {CMU Biorobotics Lab, {\normalfont Researcher for Dr. Howie Choset}}
            {Pittsburgh, PA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Led a team of 3 students in planning and implementing firmware for JumpingBot, a robot which can self-stabilize in freefall.
                \item[-] Designed and programmed an Android application which allows realtime sensor data to be accessed in MATLAB and ROS.
            \end{itemize}}
    \end{entrylist}

    \section{selected projects}

    \begin{entrylist}
        \entrys
            {2015}
            {tunemachine.co, {\normalfont Andreeseen Horowitz Battle of the Hacks 2.0}}
            {Menlo Park, CA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Implemented the backend for a Node.js web application which provides a version control system for Spotify playlists.
            \end{itemize}}
        \entrys
            {2015}
            {course-api, {\normalfont Scottylabs}}
            {Pittsburgh, PA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Developed a set of Python scripts that provide developers access to CMU course schedules, descriptions, and student evaluations.
            \end{itemize}}
        \entrys
            {2013}
            {CMUEats, {\normalfont HackCMU}}
            {Pittsburgh, PA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Wrote the backend for a web application that tracks the hours of CMU dining locations using Python, Django, and MongoDB -- later ported to Node.js.
                \item[-] A year later, the app maintained more than 400 daily hits from students.
            \end{itemize}}
    \end{entrylist}

    \section{other experience}

    \begin{entrylist}
        \entrys
            {since 2014}
            {Scottylabs}
            {Pittsburgh, PA}
            {\begin{itemize}[leftmargin=*]
                \item[-] Helped to organize and operate Tartanhacks, a hackathon of 350 students from the Pittsburgh area.
            \end{itemize}}
        \entrys
            {2013}
            {Eagle Scout, {\normalfont Boy Scouts of America}}
            {Amherst, NH}
            {\begin{itemize}[leftmargin=*]
                \item[-] Brainstormed, planned, and executed a service project that supplies used eyeglasses to developing countries. Over the course of the project, I raised more than \$650 and managed 38 volunteers.
            \end{itemize}}
    \end{entrylist}

\end{document}
